\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\geometry{margin=0.5in}
\setlist{nosep}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.4em}{0.3em}

\begin{document}
\pagenumbering{gobble}

\begin{center}
{\LARGE \textbf{Your Name Here}} \\[3pt]
\small
City, State, Country \\[2pt]
\href{mailto: youremail@example.com}{youremail@example.com},
\href{https://www.linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile}
\end{center}

\section*{\textbf{Summary}}
Data-driven business professional specializing in analytics and marketing insights; experienced in leveraging Power BI, SQL, Excel, and digital analytics tools to translate complex datasets into strategic recommendations for campaign optimization, ROI evaluation, customer segmentation, and performance reporting.

\section*{Education}
\textbf{Your University Name}, City, State \\
Master’s in Business Administration – Business Analytics \\[4pt]
\textbf{Your Undergraduate Institution}, Bachelor’s in Engineering – Field of Study

\section*{Professional Experience}

\noindent
\textbf{Graduate/Research Assistant} \hfill \textit{Month 20XX -- Present} \\
\textit{Your University, City, State}
\begin{itemize}
    \item Conducted marketing and behavioral research exploring decision-making factors influencing student enrollment.
    \item Developed a centralized contact and alumni dataset to enable segmentation and targeted program outreach.
    \item Cleaned and analyzed large datasets to uncover insights supporting recruitment strategies.
    \item Translated research findings into dashboards and visual reports for academic and administrative teams.
    \item Collaborated with faculty to source scholarly literature supporting ongoing behavioral and marketing studies.
\end{itemize}

\vspace{0.5em}

\noindent
\textbf{Operations / Production Intern} \hfill \textit{Month 20XX -- Month 20XX} \\
\textit{Company Name, City, Country}
\begin{itemize}
    \item Assisted with daily production scheduling and monitored operations to improve resource utilization.
    \item Built dashboards and analytical reports to identify inefficiencies and track key production metrics.
    \item Coordinated with quality and procurement teams to maintain consistent workflow and inventory levels.
    \item Prepared weekly operational summaries and visualizations for management review.
    \item Supported marketing initiatives by organizing internal product data and designing visual assets.
\end{itemize}

\section*{Academic / Technical Projects}

\textbf{Inventory and Logistics Management System}
\begin{itemize}
    \item Designed a SQL-based system with automated validation and workflow triggers to improve operational visibility.
    \item Enhanced data architecture to reduce discrepancies and streamline decision-making across product movement.
\end{itemize}

\textbf{Sales Analytics Dashboard}
\begin{itemize}
    \item Built an interactive Power BI dashboard analyzing tens of thousands of sales records to identify trends.
    \item Delivered insights supporting product prioritization, marketing strategy, and forecasting improvements.
\end{itemize}

\textbf{Fraud Detection Modeling}
\begin{itemize}
    \item Developed and evaluated machine learning models (e.g., XGBoost, Random Forest) for fraud classification.
    \item Applied predictive analytics and validation techniques to reduce false positives and improve detection accuracy.
\end{itemize}

\section*{Skills}
\begin{itemize}
    \item \textbf{Analytics Tools:} Power BI, SQL, Excel, Google Analytics, Python (Basic)
    \item \textbf{Marketing Techniques:} Market Research, Segmentation, A/B Testing, ROI Analysis, Campaign Optimization
    \item \textbf{Creative \& Content Tools:} Canva, MS Office Suite, Google Workspace, Basic CRM Tools
    \item \textbf{Reporting \& Visualization:} KPIs, Dashboarding, Data Storytelling, Performance Analytics
    \item \textbf{Soft Skills:} Communication, Collaboration, Problem-Solving, Adaptability
\end{itemize}

\end{document}
